Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check interacting results

    \subsection{Interacting elliptical harmonic oscillator}
        We now make a change to the simple systems in the previous section in
        order to make everything a bit more interesting. The potential in the
        one-body Hamiltonian is perturbed in the $z$-direction according to
        \autoref{eq:scaled_hamiltonian} by setting $\lambda = \sqrt{8} \approx
        2.82843$. This corresponds to enclosing particles of the simulation in
        an elliptical trap instead of a spherical trap.

        We also choose a new trial wavefunction with the elliptical gaussian
        single particle functions in \autoref{eq:scaled_spf} and the Jastrow
        factor. The hard sphere radius is set to $a/a_{\text{ho}} = 0.0043$.

        Due to similarities with the spherical harmonic oscillator
        system we make a guess that the true minimum of this new system should
        be situated close to the minimum of the previous system. Choosing seven
        values for $\alpha \in [0.2, 0.7]$ we run importance sampling on this
        system for $N = \{10, 50, 100\}$ particles in $d = 3$ dimensions using
        $2^{21}$ Monte Carlo cycles\footnote{This turned out to be a little bit
        overkill due to the fast convergence of importance sampling.} and an
        additional $10\%$ of the Monte Carlo cycles for thermalization of the
        system prior to doing any sampling. We have used $\delta t = 0.1$ yields
        a high acceptance ratio, but slower convergence.

@@

        The result of simulations with a higher number of particles, $N=50$ and
        $N=100$, are  shown in \autoref{tab:50_interacting} and
        \autoref{tab:100_interacting} respectively. We observe that the energy
        for systems of interacting particles increases rapidly as the size of
        the system increases.

>>>>

    \subsection{Interacting elliptical harmonic oscillator}
        We now make a change to the simple system in the previous section in
        order to make everything a bit more interesting. The potential in the
        one-body Hamiltonian is perturbed in the $z$-direction according to
        \autoref{eq:scaled_hamiltonian} by setting $\lambda = \sqrt{8} \approx
        2.82843$. This corresponds to enclosing particles of the simulation in
        an elliptical trap instead of a spherical trap.

        We also choose a new trial wavefunction with the elliptical gaussian
        single particle functions and the Jastrow factor. The hard sphere radius
        is set to $a = 0.0043$.

        Due to similarities with the spherical harmonic oscillator
        system we make a guess that the true minimum of this new system should
        be situated close to the minimum of the previous system. Choosing seven
        values for $\alpha \in [0.2, 0.7]$ we run importance sampling on this
        system for $N = \{10, 50, 100\}$ particles in $d = 3$ dimensions using
        $2^{21}$ Monte Carlo cycles\footnote{This turned out to be a little bit
        overkill due to the fast convergence of importance sampling.} and an
        additional $10\%$ of the Monte Carlo cycles for thermalization of the
        system prior to doing any sampling. We have used $\delta t = 0.1$ which
        yields a high acceptance ratio, but slower convergence.

@@

        The result of simulations with a higher number of particles, $N=50$ and
        $N=100$, are  shown in \autoref{tab:50_interacting} and
        \autoref{tab:100_interacting} respectively. We observe that the energy
        for systems of interacting particles increases rapidly with the size of
        the system.
